Testing cosmic isotropy and homogeneity with \textsl{Gaia} quasars

### 2022-08-04 paper/main.tex
figures and captions

\documentclass[modern]{aastex631}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper]{geometry}

@@

@@

@@

>>>>

\documentclass[modern]{aastex631}
\usepackage[utf8]{inputenc}

@@

% figure issues
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\definecolor{captiongray}{HTML}{555555}
\mdfsetup{%
  innertopmargin=2ex,
  innerbottommargin=1.8ex,
  linecolor=captiongray,
  linewidth=0.5pt,
  roundcorner=5pt,
  shadow=true,
  shadowcolor=black!05,
  shadowsize=4pt
}
\newlength{\figurewidth}
\setlength{\figurewidth}{0.75\textwidth}

% math definitions

% text definitions
\shortauthors{hogg and storey-fisher}
\shorttitle{testing isotropy and homogeneity}

@@

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/radec.png}
  \end{center}
    \caption{The full quasar sample plotted on the sky in Equatorial coordinates.
    The NGC subsample (and its associated random catalog) is colored blue and the SGC subsample is colored orange.\label{fig:radec}.}
  \end{mdframed}
\end{figure}

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/lb.png}\\
    \includegraphics[width=\figurewidth]{notebooks/lb_random.png}
  \end{center}
    \caption{The full quasar sample and a sampling of the (much larger) random catalog, plotted on the sky in Galactic coordinates.
    The sine is taken of the Galactic latitude coordinate to make the projection equal-area.
    The NGC subsample (and its associated random catalog) is colored blue and the SGC subsample is colored orange.\label{fig:lb}.}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/zhist.png}
  \end{center}
    \caption{The redshift distributions of the NGC and SGC subsamples.\label{fig:zhist}.}
  \end{mdframed}
\end{figure}

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/cumulativeDD.png}
  \end{center}
    \caption{The cumulative total number of quasar--quasar pairs as a function of separation for the NGC and SGC subsamples.
    This figure demonstrates that the fractal dimension is extremely close to 3. The small offset between the NGC and SGC comes from the differing sizes of the two regions.\label{fig:cumulative}.}
  \end{mdframed}
\end{figure}

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/corrfunc.png}
  \end{center}
    \caption{The auto-correlation of the quasars as a function of separation for the NGC and SGC subsamples.
    This figure demonstrates that the clustering amplitude is similar between the North and the South.\label{fig:corrfunc}.}
  \end{mdframed}
\end{figure}
